Towards detecting critical crowd density with Wi-Fi positioning: Case Amsterdam ArenA

### 2016-08-17 PaperOnSmoothing/draft-31052016.tex
Restyle of section on Brownian diffusion, to be continued.

Formally, for the epochs during which a mobile device is not detected we assume Brownian motion (without drift), which is defined by
% had to change X to B because I used X for the random variables above. Sorry.
\begin{equation}
\text{d}B(t)=\sigma\text{d}W(t)
\end{equation}
where $W(t)$ is a Wiener process. The density function $f(t,x)$ of the displacement of $X$ in the time interval $[0,t]$ is known, and is a normal distribution with mean $B(0)$ and variance
\begin{equation}
\text{Var(\textit{B(t)})}=\sigma^{2}t
\end{equation}
Thus, in case we have no new observations, we smooth the density estimate from the previous epoch by convolution with the normal density function. 
The variance is determined by the length $t$ of the time interval, and the walking speed of pedestrians.
[Optional: We relate $\sigma^2$ to the walking speed of pedestrians as defined by]
\begin{equation}
\sigma^2=\frac{(\Delta B)^2}{\Delta t}
\end{equation}
The walking speed of pedestrians can be related to the local crowd density via the so-called \textit{Fundamental Diagram}. 
The fundamental diagram generally states that walking speed of pedestrians is a decreasing function of the local crowd density [(Weidman 1992)].
The fundamental diagram function has been the subject of extensive study [examples].
Although all these studies agree on the decreasing form of the function, empirical studies in different countries and cultures have resulted in different forms and parameters values.

Here we use the fundamental diagram as provided by ... [?]
\marginpar{add rescaling to include information that all visitors are still inside the stadium }

>>>>

\begin{comment}
Formally, for the epochs during which a mobile device is not detected we assume Brownian motion (without drift), which is defined by
% had to change X to B because I used X for the random variables above. Sorry.
\begin{equation}
\text{d}B(t)=\sigma\text{d}W(t)
\end{equation}
where $W(t)$ is a Wiener process. The density function $f(t,x)$ of the displacement of $X$ in the time interval $[0,t]$ is known, and is a normal distribution with mean $B(0)$ and variance
\begin{equation}
\text{Var(\textit{B(t)})}=\sigma^{2}t
\end{equation}
Thus, in case we have no new observations, we smooth the density estimate from the previous epoch by convolution with the normal density function. 
The variance is determined by the length $t$ of the time interval, and the walking speed of pedestrians.
[Optional: We relate $\sigma^2$ to the walking speed of pedestrians as defined by]
\begin{equation}
\sigma^2=\frac{L^2}{\Delta t}
\end{equation}
The walking speed of pedestrians can be related to the local crowd density via the so-called \textit{Fundamental Diagram}. 
The fundamental diagram generally states that walking speed of pedestrians is a decreasing function of the local crowd density [(Weidman 1992)].
The fundamental diagram function has been the subject of extensive study [examples].
Although all these studies agree on the decreasing form of the function, empirical studies in different countries and cultures have resulted in different forms and parameters values.

Here we use the fundamental diagram as provided by ... [?]
\marginpar{add rescaling to include information that all visitors are still inside the stadium }
\end{comment}

Formally, in case we have no new observations, we smooth the probability distribution of the previous epoch by convolution with a Gaussian probability function. The width $\sigma$ of the Gaussian PDF is determined through the conceptual equivalence of this approach with assuming Brownian motion of pedestrians. Brownian motion (without drift), is given by
\begin{equation}
\text{d}B(t)=\sqrt{2D}\text{d}W(t)
\end{equation}
where $W(t)$ is a Wiener process, and $\sigma$ is related to the diffusion constant $D$ using the relationship
\begin{equation}
\sigma=\sqrt{2Dt}
\end{equation}
The variance $\sigma^2$ is thus determined by the length $t$ of the time interval (epoch), and the diffusion constant $D$, which in turn can be determined by the walking speed of pedestrians \cite{ebeling}.\\
